---
title: Time Series
author: 'Anine'
date: '2017-11-03'
slug: time-series
categories: []
tags: []
---

Hey guys! So last post we talked about Scatterplots. In this post we are going to talk about Time Series plots!

Again, remember to bring in the necessary packages with library:

```{r message=FALSE, warning=FALSE}
library(Lahman)
library(sqldf)
library(ggplot2)
```

Now that that's done, lettuce jump into it!

Say we want to see Babe Ruth's homeruns over his twenty-two seasons. This is the query we want to put in: (remember, we want to save this in **"result"**)

```{r}
query<-"SELECT yearID,HR FROM Batting WHERE playerID='ruthba01'"
result<-sqldf(query)
```

To put this information in a time series plot, we want to use the *geom_line* prompt. You can use *geom_point* as well, if you like. If not, you can either edit it out using *#* (to hide the prompt from being visualized), making the size of the points smaller (using the promt *size*), or just leaving it out of the query all together. Let me show you all three examples. 

Here it is with an altered size:

```{r}
ggplot()+
  geom_point(data=result,aes(x=yearID,y=HR),size=1)+
  geom_line(data=result,aes(x=yearID,y=HR))+
  ggtitle("Babe Ruth's Homeruns by Year")+
  xlab("Year")+
  ylab("Number of Homeruns")
```

Using the *#* symbol to edit it out:

```{r}
ggplot()+
  #geom_point(data=result,aes(x=yearID,y=HR),size=1)+
  geom_line(data=result,aes(x=yearID,y=HR))+
  ggtitle("Babe Ruth's Homeruns by Year")+
  xlab("Year")+
  ylab("Number of Homeruns")
```

Or just leaving it out all together:

```{r}
ggplot()+
  geom_line(data=result,aes(x=yearID,y=HR))+
  ggtitle("Babe Ruth's Homeruns by Year")+
  xlab("Year")+
  ylab("Number of Homeruns")
```

And there you have it! Next post, let's go over Histograms. See yah then!