---
title: Histograms
author: Anine
date: '2017-11-03'
slug: histograms
categories: []
tags: []
---

Hey there! Glad you're back. 

So far, we have covered Scatterplots and Time Series'. Now, we will be going over Histograms. Before we get started, you know the drill:

```{r message=FALSE, warning=FALSE}
library(Lahman)
library(sqldf)
library(ggplot2)
```

To make it simple, let's just look at the weight of the players and extract it from the Master table. The query should look like this:

```{r}
query<-"SELECT weight FROM Master"
result<-sqldf(query)
```

Now, let's discuss how to go about histogramming it up. First off, we are pretty much doing the same old same old with ggplot, however, instead of using *geom_point* or *geom_line*, we are going to be using *geom_histogram* (woah, shocker!).

```{r message=FALSE, warning=FALSE}
ggplot()+
  geom_histogram(data=result,aes(x=weight),color="blue",fill="white",bins=60)+
  ggtitle("Distribution of Baseball Player Bodyweight")+
  xlab("Weight of player")+
  ylab("Number of players")
```

Alright, so you may have noticed a few diferences here. 

First and foremost, we changed the color of the bars. The *color* prompt decides the color of the outline, while *fill* is the inside of the bars (pretty easy).

Second, we added *bins* and indicated that we want only **60** of them. This decides how many bars we have. So let's take a look at the histogram if we hadn't added the bins prompt:

```{r message=FALSE, warning=FALSE}
ggplot()+
  geom_histogram(data=result,aes(x=weight),color="blue",fill="white")+
  ggtitle("Distribution of Baseball Player Bodyweight")+
  xlab("Weight of player")+
  ylab("Number of players")
```

See the difference? Alright cool cool. So you can change the number of bins as well. Take a look for yourself! Create an RScript file and plop that sucker in, then play around with the number of bins shown. 

Next we will talk about barplots! 