---
title: Barplots
author: Anine
date: '2017-11-03'
slug: barplots
categories: []
tags: []
---

BARPLOTS LET'S GO!!

Can you guess our first step? Yep, bringing those fiesty little packages into our library:

```{r message=FALSE, warning=FALSE}
library(Lahman)
library(sqldf)
library(ggplot2)
```

First of all, we want to figure out what figure out what data we want to extract. Let's say we want to look at team homerun totals in 1980.

```{r}
query<-"SELECT name,HR 
FROM Teams 
WHERE yearID=1980 
ORDER BY HR "
result<-sqldf(query)


result$name<-factor(result$name,levels=result$name)
```

So, because we want to order it by homeruns, we have to add an extra line of coding to make sure that this translates correctly into ggplot. See that last line? 

**result$name<-factor(result$name,levels=result$name)**

This is used to save the information as a facter, and organize that data in a specific manner. Ggplot defaults to ordering information in alphabetical order, and this last line counteracts that default.

Now that we have the data, we want to apply it to a barplot. In this case, we are using *geom_bar* to achieve a barplot. Let's take a look:

```{r}
ggplot()+
  geom_bar(data=result,aes(x=name,y=HR),stat='identity')+
  coord_flip()+
  ggtitle("1980 Team Homerun Totals")+
  xlab("Team Name")+
  ylab("Homeruns")
```

A few things to note here:

1) We need to add the line **stat='identity'** to have all the information go through correctly

2) We used **coord_flip** to switch the x-axis and y-axis around. To make this more understandable, let's take a look at the barplot if we had not added **coord_flip** to the code:

```{r}
ggplot()+
  geom_bar(data=result,aes(x=name,y=HR),stat='identity')+
  ggtitle("1980 Team Homerun Totals")+
  xlab("Team Name")+
  ylab("Homeruns")
```

See what I mean? 

Alrighty! That wraps things up for barplots! Until next time.